The Astropy Project:

### 2017-09-29 main.tex
earth coordinates

\textbf{Key new features:}
\begin{itemize}
    \item TODO: Celestial coordinates, but now also local coordinates (via
    EarthLocation + Time). Now supports Alt-Az coordinates, observation planning
    - shoutout to astroplan
    \item TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.
    \item TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.
    \item TODO: JPL ephemerids % Who can write this? Erik?
\end{itemize}

>>>>

\textbf{Key new features:}
\begin{itemize}
    \item In addition to representing celestial coordinates, \astropypkg\
    now supports specifying positions on the Earth in a number of different
    geocentric systems with the \texttt{EarthLocation} class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).
    \item TODO: differential classes. Represent single-derivatives of
    representations. Used to store velocity information, only really useful
    attached to a representation object.
    \item TODO: Frame classes support proper motions, radial velocities. Explain
    component naming, why SkyCoord doesn't support right now, "experimental" but
    tested feature.
    \item TODO: JPL ephemerids % Who can write this? Erik?
\end{itemize}
